Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-19 snapshot_system/fast14_evaluation.tex
update efficiency results

Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC.
Deduplication efficiency is defined as the percent of duplicate chunks
which are detected and deduplicated.
The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
is defined in Table~\ref{tab:symbol}. 
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB
and  the deduplication efficiency can reach over 90\%.
When $\sigma=4\%$, the deduplication efficiency can reach 92\%. 
The loss of efficiency in VC is caused by the restriction of the total physical memory available
in the cluster to support PDS index.  
The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
for global comparison.
In all cases, VC provides similar or better deduplication efficiency than SRB.

This result shows VC can remove  a competitive amount of duplicates.
In general, our experiments show that
dirty-bit detection at the segment level  can reduce the data size to about 23\% of original data, 
which leads  about 77\% reduction.
Local search within a segment can   further reduce the data size
to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
The PDS-based cross-VM detection with $\sigma=2\% $
can reduce the  size further to 8\% of original size, namely it 
delivers additional 10.5\% reduction.

>>>>

Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC.
Our deduplication efficiency is defined as the percent of duplicate chunks
which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
is defined in Table~\ref{tab:symbol}. 
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB
and  the deduplication efficiency can reach over 96\%.
When $\sigma=4\%$, the deduplication efficiency can reach 97\%. 
The loss of efficiency in VC is caused by the restriction of the total physical memory available
in the cluster to support PDS index. 
In the extreme case if we put all the fingerprint into PDS 
index ($\sigma=100\%$) then VC will have 100\% efficiency.
The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
of duplicate detection.
Our VC approach delivers slightly worse deduplication efficiency compare to SRB, which is totally acceptable
because we are rewarded by architecture-wise benefits such as fault-tolerant and fast approximate deletion.

This result shows VC can remove  a competitive amount of duplicates.
In general, our experiments show that
dirty-bit detection at the segment level can reduce the data size to about 24\% of original data, 
which leads  about 76\% reduction.
Similarity-guided local search can further reduce the data size
to about 12\% of original size, namely it delivers additional 12\% reduction.
The PDS-based cross-VM detection with $\sigma=2\% $
can reduce the  size further to 5.6\% of original size, namely it 
delivers additional 6.4\% reduction.
